An iterated Grothendieck construction of semi-cubical types

### 2022-02-18 paper/paper.tex
Correcting missing cohbox in cohlayer and cohcube
Proof of cohcube when p=r still to be checked.
Renaming \U into \UU (the former already exists and fails on my setup).

% Type theory
\newcommand{\U}{\ensuremath{\mathscr{U}}}

@@

$$
  \begin{tikzcd}
    X_0 : \U & X_1 : \U \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] & X_2 : \U \arrow[l, "\delta^\epsilon_1" description, shift left=6] \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] \arrow[l, "\delta^\omega_1" description, shift right=6] & \ldots
  \end{tikzcd}
$$

\begin{align*}
  X_0 & : \U                                                                                                      \\
  X_1 & : X_0 \times X_0 \rightarrow \U                                                                           \\
  X_2 & : \forall a b c d, X_1 : ab \rightarrow X_1 : bc \rightarrow X_1 : cd \rightarrow X_1 : da \rightarrow \U \\
  \ldots
\end{align*}

@@

  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p,[p < r \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D)) \\(b:\mylayer{l}{n,p}(D)(d))}}{:}{\makecell{\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\omega,r}{n,p}(D)(d))(\downlayer{l,\omega,r}{n,p}(D)(d)(b)) \\ \eqett \downlayer{l,\omega,r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downlayer{l,\epsilon,q+1}{n,p}(D)(d)(b))}}

@@

  \eqnline{\cohcube{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (E:\mycubsetcomp{l}{n}(D)) \\ (d:\mybox{l}{n,p}(D)) \\ (b:\mycube{l}{n,p}(D)(E)(d))}}{:}{\makecell{\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\omega,r}{n,p}(D)(d))(\downcube{l,\omega,r}{n,p}(D)(E)(d)(b)) \\ \eqett \downcube{l,\omega,r}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downcube{l,\epsilon,q+1}{n,p}(D)(E)(d)(b))}}

>>>>

% Type theory
\newcommand{\UU}{\ensuremath{\mathscr{U}}}

@@

$$
  \begin{tikzcd}
    X_0 : \UU & X_1 : \UU \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] & X_2 : \UU \arrow[l, "\delta^\epsilon_1" description, shift left=6] \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] \arrow[l, "\delta^\omega_1" description, shift right=6] & \ldots
  \end{tikzcd}
$$

\begin{align*}
  X_0 & : \UU                                                                                                      \\
  X_1 & : X_0 \times X_0 \rightarrow \UU                                                                           \\
  X_2 & : \forall a b c d, X_1 : ab \rightarrow X_1 : bc \rightarrow X_1 : cd \rightarrow X_1 : da \rightarrow \UU \\
  \ldots
\end{align*}

@@

  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p,[p < r \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D)) \\(b:\mylayer{l}{n,p}(D)(d))}}{:}{\makecell{\overright{\cohbox{l,\epsilon,\omega,q+1,r+1}{n,p}(D)(d)}(\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\omega,r}{n,p}(D)(d))(\downlayer{l,\omega,r}{n,p}(D)(d)(b))) \\ \eqett \downlayer{l,\omega,r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downlayer{l,\epsilon,q+1}{n,p}(D)(d)(b))}}

@@

  \eqnline{\cohcube{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (E:\mycubsetcomp{l}{n}(D)) \\ (d:\mybox{l}{n,p}(D)) \\ (b:\mycube{l}{n,p}(D)(E)(d))}}{:}{\makecell{\overright{\cohbox{l,\epsilon,\omega,q+1,r+1}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\omega,r}{n,p}(D)(d))(\downcube{l,\omega,r}{n,p}(D)(E)(d)(b))) \\ \eqett \downcube{l,\omega,r}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downcube{l,\epsilon,q+1}{n,p}(D)(E)(d)(b))}}
